\section{Question 3}
\subsection{(a)}
In order to prove that $B \in \text{NP}$, we need to show that it is verifiable with a given certificate.
The certificate for this question should have the following language:
\[\text{certificate}=\{\langle C, W, V \rangle : C \subseteq S \text{ and } W,V \in \mathbb{R}\}\]
We can see that this certificate is polynomial in size as it has at most $n$ elements. Therefore, we can simply sum the weights and values and compare the sums with $W$ and $V$ for verification. This algorithm has a time complexity of $\mathcal{O}(n)$ which means
this problem is verifiable in polynomial time and a member of NP.
\subsection{(b)}
For showing that $\textsc{SubsetSum} \leq_P \textsc{Knapsack}$, we need a polynomial-time function that transforms an instance of $\textsc{SubsetSum}$ to an instance of $\textsc{Knapsack}$.
This way we can show that $\textsc{Knapsack}$ is at least as hard as $\textsc{SubsetSum}$. Given a set $S$ and target $k$ with a subset $C \subseteq S$ whose sum is equal to $k$, we can construct the \textsc{Knapsack} language as:
\begin{equation}
    \begin{aligned}
        \textsc{Knapsack}=\{\langle S', W, V \rangle : W = V\}
    \end{aligned}
\end{equation}
Where $S'$ is a set of tuples each containing a weight and a value.
For the $i$th element, both the weight ($w_i$) and the value ($v_i$) will be equal to the $i$th element of $S$.
In other words, $S'$ is achieved by duplicating $S$ and packaging each pair into tuples.
Finally, let the bounds on the sums of the weights and values ($W, V$) be equal to $k$.
This reduction function is $\mathcal{O}(n)$ in time
as it must iterate through $S$ exactly once.

In order to prove that the proposed reduction is valid, we must show that:
\[\langle S, k \rangle \in \textsc{SubsetSum} \Longleftrightarrow \langle S', W, V \rangle \in \textsc{Knapsack}\]

\textbf{Proof of $\Rightarrow$:}
Suppose there exists a $C \subseteq S$ such that $\sum C = k$. By constructing $S'$, it is guaranteed that there will be a $C' \subseteq S'$ whose
weight and value sums are exactly equal to $W$ and $V$ respectively since $W = V = k$.

\textbf{Proof of $\Leftarrow$:}
Now suppose there exists a $C' \subseteq S'$ whose weight sum is less than or equal to $W$ and whose value sum is greater than or equal to $V$. Recall that the weights and values of every element in $S'$ are equal and $V=W$.
Since $V=W$, the only way that the sum of this list can be at most $W$ and at least $V$ is if it would be exactly equal to them.
By setting a new set $S$ as $S_i=v_i$, there would be a subset $C \subseteq S$ such that $\sum C=k$ due to the condition that $W = V = k$. \\

Therefore, since $\textsc{Knapsack} \in \text{NP}$ and $\textsc{SubsetSum} \leq_P \textsc{Knapsack}$, we can conclude that the \textsc{Knapsack} problem is NP-Complete. \\

\textbf{Q.E.D}