\section{Question 2}
\subsection{(a)}
The form of the certificate are the vertices ($V$) and edges ($E$) representing the common subgraph $G_{\text{sub}}$.
The verification algorithm first affirms that the number of edges in $G_{\text{sub}}$ is at least $k$.
This can be done in polynomial time with BFS or DFS.
Next, the verifcation algorithm iterates over each edge $(u, v) \in G_{\text{sub}}$ and checks that $(u, v) \in G_1$ and $(u, v) \in G_2$.
This can be accomplished by using DFS or BFS to search for the edge in $G_1$ and $G_2$.
The DFS or BFS take $\mathcal{O}(V + E)$ time and at most $E$ edges need to be iterated over.
This makes the overall runtime of the verifcation algorithm to be $\mathcal{O}(E^2 + VE)$.
Therefore, we can verify the certificate in polynomial time.
\subsection{(b)}
Let \textsc{L-C-S} denote the longest common subgraph problem.
To show that \textsc{L-C-S} is NP-hard, we can show that $\textsc{Clique} \leq_P \textsc{L-C-S}$.
Let $\langle G, k \rangle$ be an instance of $\textsc{Clique}$,
we can construct an instance of \textsc{L-C-S} through
the following steps in polynomial time.

First, we know that by deleting edges from a clique of size $k$,
we can construct an arbitrary graph beacuse a clique of size $k$ maximizes
the number of edges. Second, We know that the number of
edges associated with a clique of size $k$ is bounded by $\mathcal{O}(k^2)$
so deleting these edges runs in polynomial time. In $G_1$,
we can delete edges in the clique to make an arbitrary subgraph of size $k$.

Creating a copy of the subgraph takes polynomial time since the graph can be
traversed in  $\mathcal{O}(V + E)$ time with DFS or BFS. Then a series of edges and nodes
can be added to the copied subgraph which also takes polynomial time to create a secondary
graph $G_2$. We need to show the following:
\[\langle G, k \rangle \in \textsc{Clique} \Leftrightarrow \langle G_1, G_2, k \rangle \in \textsc{L-C-S}\]

\textbf{Proof of $\Rightarrow$:}
If a clique of size $k$ exists in $G$, then a subgraph of size at least $k$ is guaranteed to be
in both subgraph $G_1$ and $G_2$ because the clique was modified to have an arbitrary subgraph of size $k$,
and then it was copied for graph $G_2$.

\textbf{Proof of $\Leftarrow$:}
If $G_1$ and $G_2$ both have a common subgraph of size greater than or equal to $k$, then connecting $k$ nodes between the subgraphs
yields a graph with a clique of size $k$. \\

\textbf{Q.E.D}